%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart 
     \resumeProjectHeading
          {\textbf{\href{https://www.scu.edu/engineering/undergraduate/senior-design/}{Senior Design Capstone}} $|$ \emph{Human-Computer Interaction, Design Thinking, Web Applications, Usability Testing}}{}
        \resumeItemListStart
        \resumeItem{Year-long team project to empower non-technical researchers to conduct systematic app reviews on mobile stores.}
        \resumeItem{Provide end-user guides for mental health researchers to scrape/analyze metadata for millions of Google Play apps.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{College Discord Network} {\href{https://github.com/JAVAB3ANS/scu-discord-bot}{\underline{(GitHub)}}} $|$ \emph{HTML/CSS/JS, Node JS, TypeScript, Deno, Digital Ocean, Cloudflare}}{}
          \resumeItemListStart
            \resumeItem{Automated email verification system against school domain with Discord JS chatbot, saving 52 hours of manual user authentication of over 1,100 students within online community.}
            \resumeItem{Developed {\href{https://github.com/JAVAB3ANS/discord-oauth-roles-system}{\underline{server roles dashboard}} with Discord API secured by OAuth 2.0, enabling members to select from over 140 college-oriented Discord roles while staying under Discord's global rate limit of 50 requests per second.}}
            \resumeItem{Devised kiosk-like help system with quick.db database manager, answering and logging over 130 successful interactions, driving overall satifaction between server staff and students.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Undergrad Engineering Courseload Optimizer} {\href{https://github.com/JAVAB3ANS/scu-double-dips}{\underline{(GitHub)}}} $|$ \emph{Python (Tkinter GUI, os, requests, csv)}}{}
          \resumeItemListStart
            \resumeItem{Optimized engineering course selection process using school's course availability API and hashmap algorithms.}
            \resumeItem{Generated spreadsheet of over 2,180 courses fulfilling multiple requirements across 6 academic quarters.}
            \resumeItem{Identified 4,970\% more reliable courseload options against \href{https://www.scu.edu/media/school-of-engineering/pdfs/current-student-resources/undergraduate/Useful-Double-Dips-9.20.21.pdf}{\underline{outdated university data}}.} 
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Wildfire Emergency Resources Website} {\href{https://github.com/dotimothy/scucomplexfires}{\underline{(GitHub)}}} $|$ \emph{HTML/CSS/JS, Google Analytics, Google Lighthouse}}{}
          \resumeItemListStart
            \resumeItem{Coded with team of 4 developers to craft site assisting locals affected by California's 2020 Bay Area wildfires.}
            \resumeItem{Developed server-less site with minimalist UI and dark mode feature for conserving phone battery in emergencies.}
            \resumeItem{Site boasts 20 ms response time and exceeds SEO metrics in meta information and page/link structure.}
          \resumeItemListEnd 
    \resumeProjectHeading
          {\textbf{College Admissions Calculator} {\href{https://github.com/JAVAB3ANS/sjsu-ei}{\underline{(GitHub)}}} $|$ \emph{Vue JS, Bulma CSS, Python (selenium, time, requests, flask), Google App Engine}}{}
          \resumeItemListStart
            \resumeItem{Developed search-indexed app for prospective students to gauge admission chances into majors at a state college.} 
            \resumeItem{Utilized Selenium to scrape eligibility requirement thresholds for 130+ majors into comprehensive table.}
            \resumeItem{Decreased load times by 62\%, page size by 78\%, and HTTP requests by 92\% against \href{https://www.sjsu.edu/admissions/impaction/freshmen-impaction-results/index.php}{\underline{former site}}.}
          \resumeItemListEnd 
        \resumeProjectHeading
        {\textbf{Twitter RSS Feed Scraper} {\href{https://github.com/JAVAB3ANS/twitter-rss-scraper-without-auth}{\underline{(GitHub)}}} $|$ \emph{Node JS (node-fetch, fs, xml-formatter)}}{}
            \resumeItemListStart
                \resumeItem{Developed command-line app allowing users to scrape XML feeds from \href{https://www.inputmag.com/tech/nitter-is-a-new-front-end-for-twitter-that-helps-hide-you-from-advertisers}{\underline{Nitter}} as Twitter no longer hosts RSS feed.}
                \resumeItem{Avoids ads, prevents tracking of IP and JavaScript fingerprint, and bypasses rate limits originally imposed by Twitter.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd